COMPAS Race Analysis

### 2022-04-05 final_metrics_analysis.Rmd

```{python baseline set up, warning = FALSE, message = FALSE}
from aif360.sklearn.preprocessing import ReweighingMeta, Reweighing
from sklearn.metrics import accuracy_score, confusion_matrix, plot_roc_curve, recall_score, precision_score

@@

### (Group fairness) Statistical Parity Difference

@@

print(f'[Baseline] The statistical parity difference is {stat_par_diff: .2}')

disp_impact_ratio = disparate_impact_ratio(y_test, y_pred, prot_attr='race', pos_label = 0)

print(f'[Baseline] The disparate impact ratio is {disp_impact_ratio: .2}')
# disparate impact ratio without y_pred attribute was 0.77

avg_odds_error = average_odds_error(y_test, y_pred, prot_attr='race', pos_label = 0)

print(f'[Baseline] The average odds error is {avg_odds_error: .2}')

avg_odds_diff = average_odds_difference(y_test, y_pred, prot_attr='race', pos_label = 0)

@@

@@

print(f'[Baseline] The generalized entropy error is {gen_entr_error: .2}')
```

### (Group fairness) Equal Opportunity Difference

print(f'[Baseline] The equal opportunity difference is {eq_opp_diff: .2}')

@@

# Pre-Processing Approach
```{python pre-processing set up, warning = FALSE, message = FALSE}
lr = LogisticRegressionCV(solver='lbfgs')
rew = ReweighingMeta(estimator=lr, reweigher=Reweighing('race'))
rew.fit(X_train, y_train)
y_pred_REW = rew.predict(X_test)
```

@@

```{python post-processing calibrated equal odds set up, warning = FALSE, message = FALSE}
from aif360.sklearn.postprocessing import CalibratedEqualizedOdds, PostProcessingMeta

>>>>

```{python baseline set up, include = FALSE}
from aif360.sklearn.preprocessing import ReweighingMeta, Reweighing
from sklearn.metrics import accuracy_score, confusion_matrix, plot_roc_curve, recall_score, precision_score

@@

## Group Fairness Metrics

### Statistical Parity Difference

@@

print(f'[Baseline] The statistical parity difference is {stat_par_diff: .2}')
```

### Disparate Impact Ratio

```{python group fairnesss disparate impact ratio}
disp_impact_ratio = disparate_impact_ratio(y_test, y_pred, prot_attr='race', pos_label = 0)

print(f'[Baseline] The disparate impact ratio is {disp_impact_ratio: .2}')
# disparate impact ratio without y_pred attribute was 0.77
```

### Average Odds Difference

```{python group fairnesss average odds difference}
avg_odds_diff = average_odds_difference(y_test, y_pred, prot_attr='race', pos_label = 0)

@@

### Equal Opportunity Difference

print(f'[Baseline] The equal opportunity difference is {eq_opp_diff: .2}')
```

## Individual Fairness Metrics

@@

print(f'[Baseline] The generalized entropy error is {gen_entr_error: .2}')

@@

# Pre-Processing Approach
```{python pre-processing set up, include = FALSE}
lr = LogisticRegressionCV(solver='lbfgs')
rew = ReweighingMeta(estimator=lr, reweigher=Reweighing('race'))
rew.fit(X_train, y_train)
y_pred_REW = rew.predict(X_test)
```

@@

```{python post-processing calibrated equal odds set up, include = FALSE}
from aif360.sklearn.postprocessing import CalibratedEqualizedOdds, PostProcessingMeta
